Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-03-31 Moltres.tex
Having now added delayed neutron production, we can remove the warning block.

\begin{equation}
\frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
+ \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
\nu \Sigma_{g'}^f \phi_{g'}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'} + \sum_i^I \lambda_i \chi_g^{d,i} C_i
\label{eq:neutrons}
\end{equation}

\textbf{Note that at present we do not have the neutron source term from decay
  of delayed neutron precursors. Currently coupling with precursors is only one
  way, e.g. precursors are a function of temperature and neutron flux and not
  the other way around. This reverse coupling should be added before publication.}

>>>>

\begin{equation}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
\frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
+ \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
\nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
\end{equation}
